The Cost of Exclusion: Political Discrimination and Trust Deficits in the European Union

### 2025-07-08 article/main.tex
theoretical diagram added

\author[1]{Carlos A. Toruño Paniagua}
\author[2]{Santiago Pardo González}
\affil[1,2]{\emph{The World Justice Project}}
\date{June 2025}

@@

Figure xx presents our conceptual framework, linking political discrimination, affective polarization, and institutional trust through sequential and interactive pathways. At its core is the idea that political discrimination functions as an initial grievance—eroding perceived fairness and inclusion, and in turn diminishing trust in institutions.

@@

\input{"tabs/heterogenous_effects.tex"}

@@

\input{"tabs/het_effects_dissonance.tex"}

>>>>

\author{Carlos A. Toruño Paniagua}
\author{Santiago Pardo González}
\affil{\emph{The World Justice Project}}
\date{July 2025}

@@

Figure \ref{fig:0} presents our conceptual framework, linking political discrimination, affective polarization, and institutional trust through sequential and interactive pathways. At its core is the idea that political discrimination functions as an initial grievance—eroding perceived fairness and inclusion, and in turn diminishing trust in institutions.

\begin{figure}[htbp]
\centering
\caption{Grievance-based Trust Erosion}
\label{fig:0}
\includegraphics[width=0.9\textwidth]{"viz/theoretical_diagram.png"}
\end{figure}

@@

\input{"tabs/heterogenous_effects.tex"} 
\input{"tabs/het_effects_dissonance.tex"}

@@
